Reading episode files and preparing data sets

### 2025-01-22 data-raw/01-preprocessing-episode-files.Rmd

```{r}
# Episode File
gss_e_2015 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-2015/gss-e.csv"))

# Main File
gss_m_2015 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-2015/gss-m.csv"))
```

@@

```{r}
# Episode File
gss_e_2010 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-2010/gss-12M0018-E-2010-c-24-tus-ef_F1.csv"))

# Main File
gss_m_2010 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-2010/gss-12M0018-E-2010-c-24-tus-mf_F1.csv"))
```

@@

gss_e_2010 %>%
  filter(RECID == 3) %>%
  slice(unique(c(reduce(map(which(PLACE == 14), ~ c(.x - 1, .x, .x + 1)), c)))) %>%
  dplyr::select(RECID:PLACE)

@@

```{r}
# Episode File
gss_e_2005 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-2005/gss-12M0019-E-2005-c-19-e_F1.csv"))

# Main File
gss_m_2005 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-2005/gss-12M0019-E-2005-c-19-m_F1.csv"))
```

@@

```{r}
# Episode File
gss_e_1998 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-1998/gss-12M0012-E-1998-c-12e_F1.csv"))

# Main File
gss_m_1998 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-1998/gss-12M0012-E-1998-c-12-m_F1.csv"))
```

@@

```{r}
# Episode File
gss_e_1992 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-1992/gss-12M0007-E-1992-c-7-ep_F1.csv"))

# Main File
gss_m_1992 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-1992/gss-12M0007-E-1992-c-7-m_F1.csv"))
```

@@

```{r}
# Episode File
gss_e_1986 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-1986/gss-12M0002-E-1986-c-2-ep_F1.csv"))

# Main File
gss_m_1986 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-1986/gss-12M0002-E-1986-c-2-main_F1.csv"))
```

>>>>

```{r}
# Episode File
#gss_e_2015 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-2015/gss-e.csv"))# Original file
gss_e_2015 <- read.csv(paste0(here(), "/data-raw/2015-gss-e-reproducibility.csv")) # Subset for reproducibility

# Main File
#gss_m_2015 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-2015/gss-m.csv")) # Original file
gss_m_2015 <- read.csv(paste0(here(), "/data-raw/2015-gss-m-reproducibility.csv")) # Subset for reproducibility
```

@@

```{r}
# Episode File
#gss_e_2010 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-2010/gss-12M0018-E-2010-c-24-tus-ef_F1.csv")) # Original file
gss_e_2010 <- read.csv(paste0(here(), "/data-raw/2010-gss-e-reproducibility.csv")) # Subset for reproducibility

# Main File
#gss_m_2010 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-2010/gss-12M0018-E-2010-c-24-tus-mf_F1.csv")) # Original file
gss_m_2010 <- read.csv(paste0(here(), "/data-raw/2010-gss-m-reproducibility.csv")) # Subset for reproducibility
```

@@

```{r}
gss_e_2010 %>%
  filter(RECID == 3) %>%
  slice(unique(c(reduce(map(which(PLACE == 14), ~ c(.x - 1, .x, .x + 1)), c)))) %>%
  dplyr::select(RECID:PLACE)

@@

```{r}
# Episode File
#gss_e_2005 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-2005/gss-12M0019-E-2005-c-19-e_F1.csv")) # Original file
gss_e_2005 <- read.csv(paste0(here(), "/data-raw/2005-gss-e-reproducibility.csv")) # Subset for reproducibility

# Main File
#gss_m_2005 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-2005/gss-12M0019-E-2005-c-19-m_F1.csv")) # Original file
gss_m_2005 <- read.csv(paste0(here(), "/data-raw/2005-gss-m-reproducibility.csv")) # Subset for reproducibility
```

@@

```{r}
# Episode File
# gss_e_1998 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-1998/gss-12M0012-E-1998-c-12e_F1.csv")) # Original file
gss_e_1998 <- read.csv(paste0(here(), "/data-raw/1998-gss-e-reproducibility.csv")) # Subset for reproducibility

# Main File
# gss_m_1998 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-1998/gss-12M0012-E-1998-c-12-m_F1.csv")) # Original file
gss_m_1998 <- read.csv(paste0(here(), "/data-raw/1998-gss-m-reproducibility.csv")) # Subset for reproducibility
```

@@

```{r}
# Episode File
# gss_e_1992 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-1992/gss-12M0007-E-1992-c-7-ep_F1.csv")) # Original file
gss_e_1992 <- read.csv(paste0(here(), "/data-raw/1992-gss-e-reproducibility.csv")) # Subset for reproducibility

# Main File
# gss_m_1992 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-1992/gss-12M0007-E-1992-c-7-m_F1.csv")) # Original file
gss_m_1992 <- read.csv(paste0(here(), "/data-raw/1992-gss-m-reproducibility.csv")) # Subset for reproducibility
```

@@

```{r}
# Episode File
# gss_e_1986 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-1986/gss-12M0002-E-1986-c-2-ep_F1.csv")) # Original file
gss_e_1986 <- read.csv(paste0(here(), "/data-raw/1986-gss-e-reproducibility.csv")) # Subset for reproducibility

# Main File
# gss_m_1986 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-1986/gss-12M0002-E-1986-c-2-main_F1.csv")) # Original file
gss_m_1992 <- read.csv(paste0(here(), "/data-raw/1986-gss-m-reproducibility.csv")) # Subset for reproducibility
```
